### 2020-03-12 CalNotes.tex
Work on delta=eps power

	& + 2 \psi^\epl(x) z - \psi^\epl \int_{\R} x^2 \phi^\epl(x) \partial_z R^\epl(x, z) \dd x.

@@

\begin{lemma}\label{lem:distanceZandX} Under Assumption \ref{as:regularity}, let the couple $(X^\epl, Z^\epl)^\top$ be distributed as its invariant measure $\mu^\epl$. Then, if $\delta \leq 1$, it holds for any integer $p \geq 1$
	\begin{equation}
	\E^{\rho^\epl} \abs{X^\epl - Z^\epl}^{2p} \leq C\left(\epl^{2p} + \delta^p\right),
	\end{equation}
	for a constant $C > 0$ independent of $\epl$ and $\delta$.
\end{lemma}
\begin{proof} Let us first remark that the filtering kernel satisfies
	\begin{equation}\label{eq:filterIntegral}
	\int_0^t k(t-s) \dd s = 1 - e^{-t/\delta},
	\end{equation}
	which implies that the measure $\kappa_t(\d s)$ on $(0, t)$ defined as
	\begin{equation}
	\kappa_t(\d s) \defeq \frac{k(t-s)}{1 - e^{-t/\delta}} \dd s,
	\end{equation}
	is a probability measure. Let $X_t^\epl$ be at stationarity with respect to its invariant measure, which we recall having density denoted as $\phi^\epl$. Let $Z_t^\epl$ be the corresponding filtered process. By definition of $Z^\epl_t$ and due \eqref{eq:filterIntegral} we now have
	\begin{equation}
	\begin{aligned}
	X_t^\epl - Z_t^\epl &= X_t^\epl - \int_0^t k(t-s) X_s^\epl \dd s\\
	&= \int_0^t k(t - s) \left(X_t^\epl - X_s^\epl\right) \dd s + e^{-t/\delta} X^\epl_t\\
	&= (1 - e^{-t/\delta})\int_0^t \left(X_t^\epl - X_s^\epl\right) \kappa_t(\d s) + e^{-t/\delta} X^\epl_t.
	\end{aligned}
	\end{equation}
	Therefore, Jensen's inequalities yields for a constant $C > 0$ depending only on $p$
	\begin{equation}
	\begin{aligned}
	\E^{\phi^\epl}\abs{X_t^\epl - Z_t^\epl}^{2p} &\leq C (1 - e^{-t/\delta})^{2p} \int_0^t \E^{\phi^\epl} \abs{X_t^\epl - X_s^\epl}^{2p} \kappa_t (\d s) + C e^{-2pt/\delta} \E^{\phi^\epl} \abs{X^\epl_t}^{2p}\\
	&\leq C\int_0^t \E^{\phi^\epl} \abs{X_t^\epl - X_s^\epl}^{2p} k(t-s) \dd s + Ce^{-2pt/\delta} \E^{\phi^\epl} \abs{X^\epl_t}^{2p},
	\end{aligned}
	\end{equation}
	where we replaced the definition of $\kappa(\d s)$ and exploited the fact that $1 - e^{-t/\delta}\leq 1$ for all $t \geq 0$. Due to \cite[Corollary 5.4]{PaS07}, we know that $X^\epl_t$ has bounded moments of all orders with respect to its invariant measure. Moreover, the estimate
	\begin{equation}
	\E^{\phi^\epl}\abs{X_t^\epl - X_s^\epl}^{2p} \leq C\left(\epl^{2p} + (t-s)^{2p} + (t-s)^p\right),
	\end{equation}
	holds for all $t > s$ due to \cite[Lemma 6.1]{PaS07}. Finally, it is possible to verify by induction on $r$ that for all integers $r$ it holds
	\begin{equation}
	\int_0^t k(t-s) (t - s)^r \dd s \leq r! \, \delta^r, 
	\end{equation}
	which implies that there exists a constant $C > 0$ depending only on $p$ such that
	\begin{equation}
	\E^{\phi^\epl}\abs{X_t^\epl - Z_t^\epl}^{2p} \leq C\left(\epl^{2p} + \delta^p + e^{-2pt/\delta}\right).
	\end{equation}
	Let us now remark that this result holds for $X_t^\epl$ being at stationarity and for $Z_t^\epl$ be its filtered process, and not for a couple $(X^\epl, Z^\epl)^\top \sim \mu^\epl$. In order to conclude, we remark that due to Lemma \ref{lem:ergodicity} we have for all $t \geq 0$ and for a constant $C$ depending on the initial condition and $p$  
	\begin{equation}
	\E^{\rho^\epl} \abs{X^\epl - Z^\epl}^{2p} \leq \E^{\phi^\epl}\abs{X_t^\epl - Z_t^\epl}^{2p} + Ce^{-\lambda t},
	\end{equation}
	which, for $t$ sufficiently big, yields
	\begin{equation}
	\E^{\rho^\epl} \abs{X^\epl - Z^\epl}^{2p} \leq C\left(\epl^{2p} + \delta^p\right),
	\end{equation}
	which is the desired result.
\end{proof}

@@

>>>>

	& + 2 \psi^\epl(z) z - \psi^\epl \int_{\R} x^2 \phi^\epl(x) \partial_z R^\epl(x, z) \dd x.

@@

\begin{lemma}\label{lem:distanceZandX} Under Assumption \ref{as:regularity}, let the couple $(X^\epl, Z^\epl)^\top$ be distributed as its invariant measure $\mu^\epl$. Then, if $\delta \leq 1$, it holds for any integer $p \geq 1$
	\begin{equation}
	\E^{\rho^\epl} \abs{X^\epl - Z^\epl}^{2p} \leq C\left(\epl^{2p} + \delta^p\right),
	\end{equation}
	for a constant $C > 0$ independent of $\epl$ and $\delta$.
\end{lemma}
\begin{proof} Let us first remark that the filtering kernel satisfies
	\begin{equation}\label{eq:filterIntegral}
	\int_0^t k(t-s) \dd s = 1 - e^{-t/\delta},
	\end{equation}
	which implies that the measure $\kappa_t(\d s)$ on $(0, t)$ defined as
	\begin{equation}
	\kappa_t(\d s) \defeq \frac{k(t-s)}{1 - e^{-t/\delta}} \dd s,
	\end{equation}
	is a probability measure. Let $X_t^\epl$ be at stationarity with respect to its invariant measure, which we recall having density denoted as $\phi^\epl$. Let $Z_t^\epl$ be the corresponding filtered process. By definition of $Z^\epl_t$ and due \eqref{eq:filterIntegral} we now have
	\begin{equation}
	\begin{aligned}
	X_t^\epl - Z_t^\epl &= X_t^\epl - \int_0^t k(t-s) X_s^\epl \dd s\\
	&= \int_0^t k(t - s) \left(X_t^\epl - X_s^\epl\right) \dd s + e^{-t/\delta} X^\epl_t\\
	&= (1 - e^{-t/\delta})\int_0^t \left(X_t^\epl - X_s^\epl\right) \kappa_t(\d s) + e^{-t/\delta} X^\epl_t.
	\end{aligned}
	\end{equation}
	Therefore, Jensen's inequalities yields for a constant $C > 0$ depending only on $p$
	\begin{equation}
	\begin{aligned}
	\E^{\phi^\epl}\abs{X_t^\epl - Z_t^\epl}^{2p} &\leq C (1 - e^{-t/\delta})^{2p} \int_0^t \E^{\phi^\epl} \abs{X_t^\epl - X_s^\epl}^{2p} \kappa_t (\d s) + C e^{-2pt/\delta} \E^{\phi^\epl} \abs{X^\epl_t}^{2p}\\
	&\leq C\int_0^t \E^{\phi^\epl} \abs{X_t^\epl - X_s^\epl}^{2p} k(t-s) \dd s + Ce^{-2pt/\delta} \E^{\phi^\epl} \abs{X^\epl_t}^{2p},
	\end{aligned}
	\end{equation}
	where we replaced the definition of $\kappa(\d s)$ and exploited the fact that $1 - e^{-t/\delta}\leq 1$ for all $t \geq 0$. Due to \cite[Corollary 5.4]{PaS07}, we know that $X^\epl_t$ has bounded moments of all orders with respect to its invariant measure. Moreover, the estimate
	\begin{equation}
	\E^{\phi^\epl}\abs{X_t^\epl - X_s^\epl}^{2p} \leq C\left(\epl^{2p} + (t-s)^{2p} + (t-s)^p\right),
	\end{equation}
	holds for all $t > s$ due to \cite[Lemma 6.1]{PaS07}. Finally, it is possible to verify by induction on $r$ that for all integers $r$ it holds
	\begin{equation}\label{eq:FilterTminusS}
	\int_0^t k(t-s) (t - s)^r \dd s \leq r! \, \delta^r, 
	\end{equation}
	which implies that there exists a constant $C > 0$ depending only on $p$ such that
	\begin{equation}
	\E^{\phi^\epl}\abs{X_t^\epl - Z_t^\epl}^{2p} \leq C\left(\epl^{2p} + \delta^p + e^{-2pt/\delta}\right).
	\end{equation}
	Let us now remark that this result holds for $X_t^\epl$ being at stationarity and for $Z_t^\epl$ be its filtered process, and not for a couple $(X^\epl, Z^\epl)^\top \sim \mu^\epl$. In order to conclude, we remark that due to Lemma \ref{lem:ergodicity} we have for all $t \geq 0$ and for a constant $C$ depending on the initial condition and $p$  
	\begin{equation}
	\E^{\rho^\epl} \abs{X^\epl - Z^\epl}^{2p} \leq \E^{\phi^\epl}\abs{X_t^\epl - Z_t^\epl}^{2p} + Ce^{-\lambda t},
	\end{equation}
	which, for $t$ sufficiently big, yields
	\begin{equation}
	\E^{\rho^\epl} \abs{X^\epl - Z^\epl}^{2p} \leq C\left(\epl^{2p} + \delta^p\right),
	\end{equation}
	which is the desired result.
\end{proof}

@@

\section{Some calculations}

\begin{lemma}
		Z_t^\epl - X_t^\epl = \delta (A \cdot V'(X_t^\epl)) + \ldots
\begin{proof} Let $t > s$, $\Phi$ solution of \eqref{eq:CellProblem} and $Y_t^\epl = X_t^\epl / \epl$. Then, an application of the Itô formula yields \cite[Formula 5.8]{PaS07}
	\begin{equation}\label{eq:App_DiffXtXs}
		X_t^\epl - X_s^\epl &= -\int_s^t (\alpha \cdot V'(X_r^\epl))(1 + \Phi'(Y^\epl_r)) \dd r\\
		&\quad +\sqrt{2\sigma} \int_s^t (1 + \Phi'(Y_r^\epl)) \dd W_r + \epl(\Phi(Y^\epl_t)-\Phi(Y^\epl_s)).
	Recall that we have
		X_t^\epl - Z_t^\epl = \int_0^t k(t-s) (X_t - X_s) \dd s + e^{-t/\delta}X_t.
	Plugging \eqref{eq:App_DiffXtXs} into the equation above, we obtain
		X_t^\epl - Z_t^\epl = I_1^\epl(t) + I_2^\epl(t) + I_3^\epl(t) + I_4^\epl(t),
		I_1^\epl(t) &\defeq -\int_0^t k(t-s)\int_s^t (\alpha \cdot V'(X_r^\epl))(1 + \Phi'(Y^\epl_r)) \dd r \dd s,\\
		I_2^\epl(t) &\defeq \sqrt{2\sigma}\int_0^t k(t-s) \int_s^t (1 + \Phi'(Y_r^\epl)) \dd W_r \dd s, \\
		I_3^\epl(t) &\defeq \epl \int_0^t k(t-s)(\Phi(Y^\epl_t)-\Phi(Y^\epl_s)) \dd s,\\
		I_4^\epl(t) &= e^{-t / \delta}X_t.
	Let us analyze the terms above singularly. For $I_1^\epl(t)$, one can show \cite[Proposition 5.8]{PaS07}
		 \int_s^t (\alpha \cdot V'(X_r^\epl)) (1 + \Phi'(Y^\epl_r)) \dd r = (t - s)(A \cdot V'(X_t^\epl)) + R_1^\epl(t-s),
	in law, where
	\begin{equation}\label{eq:FirstTermPavStu}
		\left(\E^{\phi^\epl}\abs{R_1^\epl(t-s)}^p\right)^{1/p} \leq C(\epl^2 + \epl(t-s)^{1/2}+(t-s)^{3/2}).
	Therefore, 
	\begin{equation}\label{eq:Diff_I1}
		I_1^\epl(t) &= -(A \cdot V'(X_t^\epl)) \int_0^t k(t-s) (t-s)\dd s + \int_0^t k(t-s)R^\epl(t-s) \dd s\\
		&= -\delta (A \cdot  V'(X_t^\epl)) + e^{-t/\delta}(t + \delta)(A \cdot V'(X_t^\epl)) + \widetilde R_1^\epl(t),
	where we exploited the equality
		\int_0^t k(t-s) (t-s) \dd s = \delta - e^{-t/\delta}(t + \delta),
	and where
		\widetilde R_1^\epl(t) \defeq \int_0^t k(t-s)R_1^\epl(t-s) \dd s.
	Now, Jensen's inequality with $\kappa(\d s)$ and the inequalities \eqref{eq:FirstTermPavStu} and \eqref{eq:FilterTminusS} yield for all integers $p \geq 1$ and a constant $C$ depending only on $p$
		\E\abs{\widetilde R_1^\epl(t)}^{2p} &= (1-e^{-t/\delta})^{2p}\E\abs{\int_0^t R_1^\epl(t-s) \kappa(\d s)}^{2p}\\
		&\leq (1-e^{-t/\delta})^{2p} \int_0^t \E \abs{R_1^\epl(t-s)}^{2p} \kappa(\d s)\\
		&\leq C (1-e^{-t/\delta})^{2p-1} \int_0^t k(t-s)(\epl^{4p} + \epl(t-s)^p+(t-s)^{3p}) \dd s\\
		&\leq C \left( \epl^{4p} + \epl \delta^p + \delta^{3p} \right).
	We now consider the second term. Let us remark that it holds \cite[Proposition 5.7, Section 6.2]{PaS07}
		\sqrt{2\sigma} \int_s^t \left(1+\Phi'(Y_s^\epl)\right) \dd W_r = \sqrt{2\Sigma}\left(\widehat W_t - \widehat W_s\right) + R_2^\epl(t-s),
	in law, where $\Sigma$ is the diffusion coefficient of the homogenized equation \eqref{eq:SDE_HOM}, $\widehat W_t$ is a standard Brownian motion and 
		\left(\E\abs{R_2^\epl(t-s)}^p\right)^{1/p} \leq C\epl^\iota,
	for all $\iota \in (0, 1/2)$. Therefore, it holds in law
		I_2^\epl(t) = \int_0^t k(t-s) \left(\widehat W_t - \widehat W_s\right) \dd s + \widetilde R_2^\epl(t),
		\widetilde R_2^\epl(t) \defeq \int_0^t k(t-s) R_2^\epl(t-s) \dd s.
	Let us now remark that applying Jensen's inequality with $\kappa(\d s)$, due to the moments of the Gaussian distribution and applying \eqref{eq:FilterTminusS}, we have for a constant $C > 0$ depending only on $p$
		\E\abs{\int_0^t k(t-s) \left(\widehat W_t - \widehat W_s\right) \dd s}^p &\leq (1-e^{-t/\delta})^{p-1} \int_0^t (2\Sigma)^{p/2}k(t-s)\E\abs{\widehat W_t - \widehat W_s}^p \dd s\\
		&\leq C \int_0^t k(t - s) (t-s)^p \dd s \\
		&\leq C \delta^p.
	Moreover, always applying Jensen's inequality with $\kappa(\d s)$ we simply obtain
		\E\abs{\widetilde R_2^\epl(t)}^p \leq C \epl^{p\iota}.
	Let us now consider $I_3^\epl(t)$. Since $\Phi$ is bounded, we simply have
		\abs{I_3^\epl(t)} \leq C \epl, 
	almost surely. Finally, due to \cite[Corollary 5.4]{PaS07}, we know that $X_t^\epl$ has bounded moments of all orders and therefore
		\E\abs{I_4^\epl(t)}^p \leq C e^{-pt/\delta},
	which concludes the proof.
